The eclipse of ASASSN-21qj: A planetary collision afterglow\\ and transit of the resultant debris cloud

### 2023-03-17 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure*}
    \centering
    \includegraphics[width=1\textwidth]{figures/blueing.pdf}
    \caption{Blueing of the $B-V$ colour during dimming.
    %
    Points show AAVSO data, and lines show models.
    %
    The dashed line is a line of $A_\lambda/A_V$ for the value shown in the legend in each panel, and the solid line is a model that includes an underlying scattered light component with $s=7.5$\% of the stellar flux.}
    \label{fig:blueing}
%    \script{blueing.py}
\end{figure*}

>>>>

%\begin{figure*}
 %   \centering
 %   \includegraphics[width=1\textwidth]{figures/blueing.pdf}
 %   \caption{Blueing of the $B-V$ colour during dimming.
 %   %
 %   Points show AAVSO data, and lines show models.
 %   %
 %   The dashed line is a line of $A_\lambda/A_V$ for the value shown in the %legend in each panel, and the solid line is a model that includes an underlying scattered light component with $s=7.5$\% of the stellar flux.}
  %  \label{fig:blueing}
%    \script{blueing.py}
%\end{figure*}
